A Generic and Efficient E-field Parallel Imaging Correlator for Next-Generation Radio Telescopes

### 2015-11-06 imaging_demo/ms.tex
Update abstract with minor suggestions from Adam
From 70146f3 (master):
=====================

In ms.tex,

(*) Update abstract with suggestions from Adam

% Abstract of the paper
\begin{abstract}
Modern radio telescopes are favoring densely packed array layouts consisting of 
large numbers of antennas ($\Nant\gtrsim 1000$). Since the complexity of 
traditional correlators scales as $\mathcal{O}(\Nant^2)$, there will be a steep 
cost for realizing the full imaging potential of these powerful instruments. 
Through our generic and efficient E-field Parallel Imaging Correlator (EPIC), 
we present the first software demonstration of a generalized direct imaging 
algorithm known as the Modular Optimal Frequency Fourier (MOFF) imager. It takes 
advantage of the multiplication-convolution theorem of Fourier transforms. Not 
only does it bring down the cost for dense layouts to 
$\mathcal{O}(\Nant\log_2\Nant)$ but can also image from irregularly arranged 
heterogeneous antenna arrays. EPIC is highly modular and parallelizable, 
implemented in object oriented Python, and publicly available. We have verified 
the images produced to be equivalent to those produced using traditional 
techniques. We have also validated our implementation on data observed with the 
Long Wavelength Array (LWA). Antenna systems with a dense filling factor 
consisting of a large number of antennas such as LWA, the Square Kilometre Array, 
Hydrogen Epoch of Reionization Array, and Canadian Hydrogen Intensity Mapping 
Experiment will gain significant advantage by deploying EPIC. Inherent 
availability of calibrated time-domain images on timescales roughly equal to the 
writeout timescale of the digitizer and vastly lower bandwidth relative to 
visibility based systems will make it a prime candidate for transient searches 
of Fast Radio Bursts (FRB) as well as planetary and exoplanetary phenomena. 
\end{abstract}

>>>>

% Abstract of the paper
\begin{abstract}
Modern radio telescopes are favoring densely packed array layouts consisting of 
large numbers of antennas ($\Nant\gtrsim 1000$). Since the complexity of 
traditional correlators scales as $\mathcal{O}(\Nant^2)$, there will be a steep 
cost for realizing the full imaging potential of these powerful instruments. 
Through our generic and efficient E-field Parallel Imaging Correlator (EPIC), 
we present the first software demonstration of a generalized direct imaging 
algorithm, namely, the Modular Optimal Frequency Fourier (MOFF) imager. It takes 
advantage of the multiplication-convolution theorem of Fourier transforms. Not 
only does it bring down the cost for dense layouts to 
$\mathcal{O}(\Nant\log_2\Nant)$ but can also image from irregularly arranged 
heterogeneous antenna arrays. EPIC is highly modular and parallelizable, 
implemented in object oriented Python, and publicly available. We have verified 
the images produced to be equivalent to those produced using traditional 
techniques to within a precision determined by coarseness of gridding. We have 
also validated our implementation on data observed with the Long Wavelength Array 
(LWA). Antenna layouts with a dense filling factor consisting of a large number 
of antennas such as LWA, the Square Kilometre Array, Hydrogen Epoch of 
Reionization Array, and Canadian Hydrogen Intensity Mapping Experiment will gain 
significant computational advantage by deploying EPIC. Inherent availability of 
calibrated time-domain images on timescales roughly equal to the writeout 
timescale of the digitizer and vastly lower I/O bandwidth relative to visibility 
based systems will make it a prime candidate for transient searches of Fast Radio 
Bursts (FRB) as well as planetary and exoplanetary phenomena. 
\end{abstract}
